Detecting Facial Expressions in Professional Tennis Matches

### 2017-06-30 Report06-12.Rmd
New Image with Face Box plot
geom_tile, and EBImage used to overlay rectangles on faces

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
  for(i in imgList){
    img <- image_read(paste0("figures/", i))

    p <- ggplot(data.frame(x=c(0,800), y=c(0,450)), aes(x,y)) +
      theme_void()+ coord_fixed()+
      annotation_custom(rasterGrob(img)) +
      coord_cartesian(xlim=c(0, 800), ylim=c(0,450))

    faceData <- ALLmetaIMGnamedFaces %>% filter(file == i)

    if(nrow(faceData) == 0){
      print(p)
      next
    } else{

      faceData <- faceData %>%
        mutate(x1 = minX, x2 = minX, x3 = maxX, x4 = maxX, x5 = minX,
               y1 = minY, y2 = maxY, y3 = maxY, y4 = minY, y5 = minY) %>%
        gather(corner, boxPos, x1:y5) %>%
        mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
        dplyr::select(-corner) %>% spread(posCoord, boxPos)

    }
    if(matchBox){
      p <- p + geom_path(aes(x=x, y=450-y, group = c(type, boxID), colour=boxID), faceData) + guides(colour="none")
    }
    else{
      p <- p + geom_path(aes(x=x, y=450-y, group = c(FaceID), colour=type), faceData) + scale_color_manual(values = c(Skybiometry="#ffe093", Microsoft="#5cc3f6", Google="#5cba82", Animetrics="#FF959c", Manual="#db70ff"))
    } 
  print(p)
  }
}

@@

##Introduction

>>>>

#plot images with overlaid boxes
overlayGgplot <- function(imgList, mergeData, matchBox=FALSE){
  for(i in imgList){

    #read in image
    image <- readImage(paste0("figures/", i))

    #convert image to a df, add hex value
    image_df <- data.frame(x=rep(1:nrow(image), ncol(image)),
                           y=rep(1:ncol(image),
                                 rep(nrow(image),
                                     ncol(image))),
                           r=as.vector(image[,,1]),
                           g=as.vector(image[,,2]),
                           b=as.vector(image[,,3]))
    image_df$h <- rgb(image_df[,3:5])

    #Create the plot of the image
    p <- ggplot() +
      scale_fill_identity() + 
      geom_tile(data=image_df, aes(x,-y, fill=h)) + 
      theme_void()

    # Find associated Face Box information for specific image
    faceData <- ALLmetaIMGnamedFaces %>% filter(file == i)

    if(nrow(faceData) == 0){
      return(p)
    } else{

      faceData <- faceData %>%
        mutate(x1 = minX, x2 = minX, x3 = maxX, x4 = maxX, x5 = minX,
               y1 = minY, y2 = maxY, y3 = maxY, y4 = minY, y5 = minY) %>%
        gather(corner, boxPos, x1:y5) %>%
        mutate(posCoord = substr(corner, 1, 1), posID = substr(corner, 2, 2)) %>%
        dplyr::select(-corner) %>% spread(posCoord, boxPos) %>% 
        dplyr::select(file, type, minX, maxX, minY, maxY, FaceKey, FaceID, posID, x, y)
    }

  }
  if(matchBox){
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=FaceKey, group=FaceID), fill=NA) +
      guides(colour = "none")
  }
  else{
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=type, group=FaceID), fill=NA) +
      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") + 
      coord_fixed(ratio=0.85)
    }

  return(p1)
}

@@

#Introduction
